What's in a Domain? Anaylsis of URL Features

### 2022-09-21 paper/paper.tex
Literature review work

Multiple data science and machine learning applications on internet data 
Write a literature review \cite{Vazhayil2018}
\cite{Canali2011}
\cite{Ayes2019}
\cite{Mamun2016}
\cite{Li2020}
\cite{Basnet2012}
\cite{Basnet2014}
\cite{Tupsamudre2019}
\cite{Le2018}
\cite{Baykan2009}
\cite{Kan2005}
\cite{Hernandez2012}
\cite{Chung2010}
\cite{Qiu2020}
\cite{Vaishnavi2021}
\cite{Xu2021}
\cite{Rhea2022}
\cite{Ma2009}
\cite{Verma2017}
\cite{Sountharrajan2020}

Common approaches to feature engineering on URLs include string patterns and regular expressions to
identify key sequences \cite{}, n-gram models \cite{Baykan2009}, 
the generation of task specific embedding vectors\cite{Qiu2020} and the
usage of domain name servers or registrars for ancillary information \cite{}

>>>>

Multiple data science and machine learning applications on internet data 
Write a literature review \cite{Vazhayil2018}
\cite{Canali2011}
\cite{Ayes2019}
\cite{Mamun2016}
\cite{Li2020}
\cite{Basnet2012}
\cite{Basnet2014}
\cite{Tupsamudre2019}
URLnet learns word and charcater embedings \cite{Le2018}
\cite{Baykan2009}
\cite{Kan2005}
\cite{Hernandez2012}
\cite{Chung2010}
\cite{Qiu2020}
\cite{Vaishnavi2021}
\cite{Xu2021}
\cite{Rhea2022}
\cite{Ma2009}
\cite{Verma2017}
\cite{Sountharrajan2020}
Classify Web pages based on URLs from the 4 Universities WebKB dataset. Comparing features derived from segmentation
of the URL to features derived from either link anchor text or the web page document itself \cite{Kan2004}.

Common approaches to feature engineering on URLs include string patterns and regular expressions to
identify key sequences \cite{Kan2004}, n-gram or bag of words models \cite{Baykan2009}, 
the generation of task specific embedding vectors\cite{Le2018,Qiu2020} and the
usage of domain name servers or registrars for ancillary information \cite{}. Some authors have 
empahsized that URLs are sequences of characters and require features that respect this ordering\cite{Le2018}.
However, the ordering of key features within URLs is predominantly fixed.
